Cores from kicks: constraints for observations of gravitational recoil in elliptical galaxies

### 2023-10-03 papers/paper-corekick/paper-corekick.tex
Place-holder figures for core paper

\drafting{Atte: mergers of unequal mass ratio?}

@@

>>>>

\drafting{Atte's runs of mergers of unequal mass ratio?}

\drafting{Kicks randomly orientated?}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{dag}
    \caption{Directed acyclic graph of Bayesian hierarchical factor model.}
    \label{fig:dag}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{density}
    \caption{Density profiles with errors for select representative runs.}
    \label{fig:density}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{vk_rb}
    \caption{Relation and fit between core radius and kick velocity.}
    \label{fig:vkrb}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{rb_pdf}
    \caption{Probability density function of core radius, where kick velocity is MC sampled from Zlochower relation, and pumped through our fitted model in \autoref{fig:vrkb}.}
    \label{fig:rb_pdf}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{h4}
    \caption{$h_4$ kinematic maps of pre-merger and select remnants, possible to observe signature of kick in here? (Thorsten believes yes...)}
    \label{fig:h4}
\end{figure*}
